VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_eval.tex
updated eval section. Expanded all USENIX bib entries to use proper conference name

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machine nodes failed in a cluster with $p=100$ physical machines.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and thus calculate the average availability of VM snapshots.
The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. With differnet $p$ values, how the availability varies when 
the number of failures in the cluster changes.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
settings
and
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
duplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all deduplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%.
When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
more index space is allocated  per machine for  PDS fingerprint lookup.
% increases from 100MB to 200MB per physical machine as discussed later. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

Column 2 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
using PDS and it achieves 93.02\%, missing about 3-3.56\% of the original data. That is losing upto
356GB per physical machine because every machine deals with about 10TB data of snapshots. 
Column 1 of Table~\ref{fig:efficiency-comparison} shows deduplication efficiency of VC without 
local similarity search.
%There is a big efficiency drop in this curve when the number of VMs is about 30.
The reason similarity search provides such an improvement is that
%Without this (i.e. when we only 
there are VMs in which
data  segments are moved to another location on disk, for example when a file is rewritten
rather than modified in place,  
and a dirty-bit or offset-only based detection would not be able to detect such a movement.
We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently.
In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.

@@

{\bf Memory usage with multi-VM processing and disk bandwidth with  I/O throttling}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each machine with $\sigma=2\%$. 
Table ~\ref{tab:resource_usage} gives the resource usage  when
running 1 or multiple  VM backup tasks at the same time on each physical machine. 
``CPU'' column is the percentage of a single core used. 
``Mem'' column includes 100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
receipt metadata and cache. 
``Read'' column is controlled as 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
``Write'' column is the I/O write usage of QFS and notice that each QFS write triggers disk writes in multiple machines due to
data replication.     50MB/s dirty segment read speed triggers about 16.4MB/s disk write for non duplicates with one backup task.
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
%memory during duplicate detection.

@@

{\bf Processing Time breakdown}.
Table~\ref{tab:vc_srb_combined} shows
the  average  processing  time of  a VM segment under VC and Stateless Routing with Binning (SRB). 
VC uses $\sigma=2\%$ and $4\%$.
For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time. 
It has a breakdown of processing time.
``Read/Write'' includes snapshot reading and writing from disk, and 
updating of the metadata.
``Network'' includes the cost of transferring raw and meta data from one machine to another during 
snapshot read and write.
``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
This includes PDS data lookup for VC and index lookup from disk in SRB after Bloom filter lookup.
The network transfer time for VC and SRB is about the same, because the 
amount of raw data they transfer is comparable.
SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
 while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
SRB also has a higher cost for index access and fingerprint comparison because most chunk fingerprints are routed
to remote machines for comparison while   VC handles most chunk fingerprints locally.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of software layer
when when I/O throttling is not applied to control the usage.
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
``QFS'' column is the write request traffic to the underlying file system after compression.
For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
after compression.  The underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46GB/second 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset with 1TB per machine to backup snapshots of 25 VMs, each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.

>>>>

 Table~\ref{tab:vm-availability} shows the availability of VM snapshots when 
there are up to 20 machines failed in a cluster with $p=100$ physical machines.
The trace driven execution allows us to estimate the number of file blocks shared by each VM in the VO and VC approaches
and thus calculate the average availability of VM snapshots.
The availability for  a 1000-node cluster is also listed, assuming file block sharing patterns among VMs remain
the same from $p=100$ setting to $p=1000$. With differnet $p$ values, how the availability varies when 
the number of failures in the cluster changes.

@@

Table~\ref{tab:efficiency-comparison} shows the deduplication efficiency for SRB and VC with different 
settings.
% <<<<<<< HEAD
% Our deduplication efficiency is defined as the percent of duplicate chunks
% which are detected and deduplicated, so only global perfect deduplication can have 100\% efficiency.
% The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
% is defined in Table~\ref{tab:symbol}. 
% =======
Deduplication efficiency is defined as the percent of duplicate chunks which are removed
compared to a perfect scheme which detects and removes  all deduplicates. 
% so only global perfect deduplication can have 100\% efficiency.
% We also compare several PDS sizes chosen for VC.
%(see Table~\ref{tab:symbol} for definition of ``$\sigma=2\%$'')
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
Notice $\sigma$ is the percentage of unique chunks selected in PDS.
With $\sigma =2\%$, Column 3 shows its 
%memory usage for PDS index lookup per machine is about 100MB per machine and  the 
deduplication efficiency can 
reach over 96\%.
When $\sigma=4\%$, Column 4 shows that the deduplication efficiency can reach 96.6\% while 
more index space is allocated  per machine for  PDS fingerprint lookup.
% increases from 100MB to 200MB per physical machine as discussed later. 
%and  the deduplication efficiency can reach 96.489\%.
%When $\sigma=4\%$, the deduplication efficiency can reach 97.027\% while space consumption increases to 200MB per machine. 
The loss of efficiency in VC is caused by the restriction of the physical memory available
in the cluster for fast in-memory PDS index lookup. 
%In the extreme case if we put all the fingerprint into PDS 
%index ($\sigma=100\%$) then VC will have 100\% efficiency.
SRB in Column 5 can deliver up to 97.86\% deduplication efficiency, which is slightly better than VC.
Thus this represents a tradeoff that VC provides better fault tolerance and fast approximate deletion
with a slight reduction in deduplication efficiency.

@@

Column 2 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
using PDS and it achieves 93.02\%, missing about 3-3.56\% of the original data. That is losing upto
356GB per physical machine because every machine deals with about 10TB data of snapshots. 
Column 1 of Table~\ref{tab:efficiency-comparison} shows deduplication efficiency of VC without 
local similarity search.
%There is a big efficiency drop in this curve when the number of VMs is about 30.
The reason similarity search provides such an improvement is that
%Without this (i.e. when we only 
there are VMs in which
data  segments are moved to another location on disk, for example when a file is rewritten
rather than modified in place,  
and a dirty-bit or offset-only based detection would not be able to detect such a movement.
We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently.
In general, adding local similarity-guided search increases deduplication efficiency from 94\% to over 96\%.
That is one significant improvement compared to the work in ~\cite{WeiZhangIEEE}
which uses the parent segment at the same offset to detect duplicates instead of similarity-guided search.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about a 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers an additional 12.09\% reduction.
% The PDS-based global duplicate detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers an additional 3.45\% reduction.

@@

{\bf Memory usage with multi-VM processing and disk bandwidth with  I/O throttling}. 
We have further studied the memory and disk bandwidth usage 
when running concurrent VM snapshot backup on each machine with $\sigma=2\%$. 
Table ~\ref{tab:resource_usage} gives the resource usage  when
running 1 or multiple  VM backup tasks at the same time on each physical machine. 
``CPU'' column is the percentage of a single core used. 
``Mem'' column includes 100MB memory usage for PDS index and other space cost for executing deduplication tasks such as 
recipe metadata and cache. 
The ``Read'' column is controlled to 50MB/s bandwidth usage with I/O throttling so that other cloud services are not impacted too much.
The peak raw storage read performance is about 300MB/s and we only use 16.7\% with this collocation consideration.
``Write'' is the I/O write usage of QFS; note that each QFS write triggers disk writes in multiple machines due to
data replication.     50MB/s dirty segment read speed triggers about 16.4MB/s disk write for non duplicates with one backup task.
% [ NOT REASONABLE: Notice that memory and CPU used by PDS index and QFS are not included since they belong to 
% the cloud infrastructure services and are shared among many applications.]
%We see our hybrid deduplication scheme only occupies a small amount of system resources. 
%The  local deduplication only needs to keep the parent snapshot recipe and a few similar segment recipes in 
%memory during duplicate detection.

@@

{\bf Processing Time breakdown}.
Table~\ref{tab:vc_srb_combined} shows
the  average processing  time breakdown of  a VM segment under VC and Stateless Routing with Binning (SRB). 
VC uses $\sigma=2\%$ and $4\%$.
For VC, the change of $\sigma$ does not significantly affect the overall backup speed as
PDS lookup takes only a small amount of time. 
It has a breakdown of processing time.
``Read/Write'' includes snapshot reading and writing from disk, and 
updating of the metadata.
``Network'' includes the cost of transferring raw and meta data from one machine to another during 
snapshot read and write.
``Index Lookup'' is the disk, network and CPU time during fingerprint comparison.
This includes PDS data lookup for VC and index lookup from disk in SRB after Bloom filter lookup.
The network transfer time for VC and SRB is about the same, because the 
amount of raw data they transfer is comparable.
SRB spends slightly more time for snapshot read/write because during each snapshot  backup, SRB involves many small bins,
 while VC only involves few containers with a bigger size. Thus, there are more opportunities for I/O aggregation in VC to reduce seek time.
SRB also has a higher cost for index access and fingerprint comparison because most chunk fingerprints are routed
to remote machines for comparison while   VC handles most chunk fingerprints locally.

@@

{\bf Throughput of software layers without I/O throttling.}
Table~\ref{tab:throughput} shows the  average throughput of the software layer
when when I/O throttling is not applied to control usage. The
%machine when all machine nodes execute one or multiple MV backup tasks.
``Backup'' column is the throughput  of the backup service  per machine.
``Snapshot store" is the  write throughput of the snapshot store layer and the significant reduction from this
column to  ``Backup" column is caused by deduplication.
Only non-duplicate chunks trigger a snapshot store write.
``QFS'' is the write request traffic to the underlying file system after compression.
For example, with 148MB/second write traffic to the snapshot store, QFS write traffic is about 35.3MB/second
after compression.  The underlying disk storage traffic will be three times greater with replication.
The result shows that the backup service can deliver up to 5.46GB/second 
per machine without I/O restriction
under 6 concurrent backup tasks. 
For our dataset with 1TB per machine to backup snapshots of 25 VMs, each machine
would complete the backup in about 3.05 minutes.
With a higher disk storage bandwidth available, the above backup
throughput would be higher. 
%With 50MB/second controlled I/O bandwidth, each machine can deliver 171MB/second with 1 backup task and can complete the backup of 25 VMs per machine in less than 1.31 hours.
